---
title: "p8105_hw1_as6445"
output: html_document
date: "2022-09-22"
---

# Problem 1

I  will be loading the penguins dataset below. 

```{r data}
data("penguins", package = "palmerpenguins")
```

The data frame has `r nrow(penguins)` rows. The data frame has `r ncol(penguins)` columns. The column names include species, island, bill length in mm, bill depth in mm, fliper length in mm, body mass in grams, sex, and year. I can take the mean of flipper length which is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

I will now create a scatterplot showing the relationship between bill length(x) and flipper length(y) using `ggplot`. I used `aes` to assign the x and y-axis. I also included `color=species` to see the points by the species categories. 

I will also be saving the scatterplot using `ggsave` to export the plot to a pdf. I have chosen a format of my choice.

```{r scatterplot}
library(tidyverse)

ggplot(penguins, aes(x=bill_length_mm,y=flipper_length_mm, color=species))+geom_point()

ggsave("penguins.pdf")
```

# Problem 2

We are creating a data frame down below! The data frame will include four vectors any uses the `tibble` function. I have assigned random variables to create the character vector and assigned categories of my choice for the factor vector. 

```{r dataframe}
hwk_df=
  tibble(
    x=rnorm(n=10),
    y= x>0,
    z= c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    w= factor(c("high", "medium", "low","high", "medium", "low","high", "medium", "low","high" ))
  )

hwk_df
```

The mean of the sample is `r mean(pull(hwk_df, x))`. The mean of the sample is `r mean(pull(hwk_df, y))`. The mean of the sample is `r mean(pull(hwk_df, z))`. The mean of the sample is `r mean(pull(hwk_df, w))`.

The code outputs the mean for x which is numerical, and the code also outputs the mean for y which is logical. The code does not output the mean for z and w because the arguments are not numerical or logical.

## Converting variables from diff types

In a new code chunk, I used `as.numeric`to convert variables from one type to another. 

```{r convert, results='hide'}

as.numeric(hwk_df$x)
as.numeric(hwk_df$y)
as.numeric(hwk_df$z)
as.numeric(hwk_df$w)
```

After applying `as.numeric`, x,y, and z outputted numbers. Regarding y and z, the variables were converted into numbers based on the categories. This explains why it is possible to take the mean of a logical variable. However, w did not produce a numeric result and outputted a warning message saying NAs introduced by coercion. 