---
title: "p8105_hw1_as6445"
output: html_document
date: "2022-09-22"
---
# Problem 1
```{r data}
data("penguins", package = "palmerpenguins")
```

The data frame has `r nrow(penguins)` rows. The data frame has `r ncol(penguins)` columns. The column names include species, island, bill length in mm, bill depth in mm, fliper length in mm, body mass in grams, sex, and year. I can take the mean of flipper length which is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

# Problem 1

Below is the scatterplot showing the relationship between bill length(x) and flipper length(y).

```{r scatterplot}
library(tidyverse)

ggplot(penguins, aes(x=bill_length_mm,y=flipper_length_mm, color=species))+geom_point()

ggsave("penguins.pdf")
```

# Problem 2

We are creating a data frame down below!

```{r dataframe}
hwk_df=
  tibble(
    x=rnorm(n=10),
    y= x>0,
    z= c("My", "name", "is", "Ayako", "and", "here", "are", "random", "words", "listed"),
    a= factor(c("high", "medium", "low","high", "medium", "low","high", "medium", "low","high" ))
  )

hwk_df
```
The mean of the sample is `r mean(pull(hwk_df, x))`. The mean of the sample is `r mean(pull(hwk_df, y))`. The mean of the sample is `r mean(pull(hwk_df, z))`. The mean of the sample is `r mean(pull(hwk_df, a))`.

The code outputs the mean for x which is numerical, and the code also outputs the mean for y which is logical. The code does not output the mean for z and a because the arguments are not numerical or logical.

# Converting variables from diff types
```{r convert, results='hide'}

as.numeric(hwk_df$x)
as.numeric(hwk_df$y)
as.numeric(hwk_df$z)
as.numeric(hwk_df$a)
```
After applying the as.numeric function, x,y, and z outputted numbers. Regarding y and z, the variables were converted into numbers based on the categories. This explains why it is possible to take the mean of a logical variable. However, a did not produce a numeric result and outputted a warning message saying NAs introduced by coercion. 